Systematic review of outbreak response models: data analysis

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_by_collab_type.Rmd
Revised the header (title, date, authors)

---
title: "Systematic review of outbreak response models"
author: "James Azam"
date: "01/06/2021"
output:
  word_document:
    keep_md: yes
#  html_notebook
---

>>>>

---
title: "Systematic review of outbreak response models: data analysis"
author: "James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari"
date: today()
output:
  word_document:
    keep_md: yes
#  html_notebook
---
